Curation of NYC 311 Request Open Data

### 2023-06-05 talk/slides.Rmd

```{r read}
d311 <- read.csv("../data/test_sample4.csv", header = TRUE)
names(d311) <- makeColNamesUserFriendly(names(d311))
dim(d311)
tail(names(d311))
```

@@

```{r byAgency}
sort(table(d311$agency), decreasing = TRUE)
```

@@

## code agency by integer
object.size(d311$agency)
agency_code <- rep(1:14, table(d311$agency))
object.size(agency_code)
```

# Suggestions on Open Data Releasing Protocols

@@

>>>>

```{r read}
d311 <- read.csv("../data/311_202303.csv", header = TRUE)
names(d311) <- makeColNamesUserFriendly(names(d311))
dim(d311)
tail(names(d311))
```

@@

```{r byAgency}
d311freq_agency <- table(d311$agency)
sort(d311freq_agency, decreasing = TRUE)
```

@@

## code agency by integer
object.size(d311$agency)
agency_code <- rep(seq(length(d311freq_agency)), d311freq_agency)
object.size(agency_code)
```

# Conclusion

@@

## Discussion

+ something
+ something else
